---
title: "Assignment_Activity"
author: "jimmyhuang0912"
date: "June 29, 2018"
---
## Code for reading in the dataset and/or processing the data

1. Load the data
2. Process/transform the data (if necessary) into a format suitable for your analysis

```{r}
data <- read.csv(file="activity.csv", header=TRUE)
```

## Mean Total Number of Steps Taken per Day

1. Calculate the total number of steps taken per day
2. If you do not understand the difference between a histogram and a barplot, research the difference between them. Make a histogram of the total number of steps taken each day


```{r, message=FALSE, warning=FALSE}
install.packages("dplyr",repos="http://cran.rstudio.com/")
library("dplyr")
date <- group_by(data, date)
data1 <- summarize(date, totalsteps = sum(steps,na.rm=TRUE))
hist(data1$totalsteps, 
     main="Total Number of Steps Taken Each Day", 
     xlab="Total Steps per Day")
```

3. Calculate and report the mean and median of the total number of steps taken per day

```{r}
meantotal <- mean(data1$totalsteps)
mediantotal <- median(data1$totalsteps)
```

- Mean Number of Steps Taken per Day = `r meantotal`
- Median Number of Steps Taken per Day = `r mediantotal`

## Averag Daily Activity Pattern

1. Make a time series plot (i.e. \color{red}{\verb|type = "l"|}type="l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r}
int <- group_by(data, interval)
data2 <-summarize(int, meansteps = mean(steps,na.rm=TRUE))
plot(data2$interval, data2$meansteps, type="l", 
     main="Daily Activity Pattern", 
     xlab="5 Min Internval", ylab=" Average Steps")
data2[which.max(data2$meansteps),]
```

## Missing Value

1. Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with \color{red}{\verb|NA|}NAs)
2. Devise a strategy for filling in all of the missing values in the dataset. The strategy does not need to be sophisticated. For example, you could use the mean/median for that day, or the mean for that 5-minute interval, etc.
3. Create a new dataset that is equal to the original dataset but with the missing data filled in.
4. Make a histogram of the total number of steps taken each day and Calculate and report the mean and median total number of steps taken per day. Do these values differ from the estimates from the first part of the assignment? What is the impact of imputing missing data on the estimates of the total daily number of steps?

```{r}
numNA <- sum(is.na(data$steps))
numNA
data3 <- data %>% group_by(interval) %>% 
  mutate(meansteps=mean(steps,na.rm=TRUE))
for (i in 1:17568){
  if(is.na(data3$steps[i])) {
  data3$steps[i] = data3$meansteps[i]  
  }
}
data3 <- ungroup(data3)
data3 <- select(data3,-(meansteps))

date <- group_by(data3, date)
data4 <- summarize(date, totalsteps = sum(steps,na.rm=TRUE))
hist(data4$totalsteps, 
     main="Total Number of Steps Taken Each Day", 
     xlab="Total Steps per Day")
meantotal2 <- mean(data4$totalsteps)
mediantotal2 <- median(data4$totalsteps)
```

- Mean Number of Steps Taken per Day = `r meantotal2`
- Median Number of Steps Taken per Day = `r mediantotal2`

## Weekday and Weekend

1. Create a new factor variable in the dataset with two levels - "weekday" and "weekend" indicating whether a given date is a weekday or weekend day.
2. Make a panel plot containing a time series plot (i.e.type="l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all weekday days or weekend days (y-axis). See the README file in the GitHub repository to see an example of what this plot should look like using simulated data.

```{r, message=FALSE, warning=FALSE}
data3$date <- as.Date(data3$date)
dataA <- mutate(data3,day=weekdays(date))
for (i in 1:17568){
  if(dataA$day[i] %in% c('Monday', 'Tuesday', 'Wednesday', 'Thursday', 'Friday')) {
    dataA$day[i] = "Weekday"  
  }
  else if(dataA$day[i] %in% c('Saturday', 'Sunday'))
    dataA$day[i] = "weekend"
}
dataB <- aggregate(steps ~ interval + day, dataA,mean)
install.packages("ggplot2",repos="http://cran.rstudio.com/")
library("ggplot2")
ggplot(data = dataB, aes(x = interval, y = steps)) + 
  geom_line() +
  facet_grid(day ~ .) +
  ggtitle("Average Daily Activity Pattern") +
  xlab("5 Min Interval") +
  ylab("Average Steps")
```
